Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-03-07 paper/SupMat.Rnw
loading in se4qij

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
se3qij <- readRDS(file="../results_numeric/fig3qijmaxse.RDS")
@

@@

%***DAN: The code does not yet produce this figure. Eventually it needs to.
%NOTE: I have assumed this figure will look substantially the same as the corresponding main text 
%figure when I wrote the Results. If it does not, then some revisions will be needed.
\begin{figure}
%\includegraphics[width=\textwidth]{../results_figs/decompFigLBqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig4} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig4} of the main text, but using 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(0,5)}, so are not displayed.}\label{fig:fig4_alt}
%***DAN: jasmin, once the se is generated and saved by your code, the chunk at the outset of this 
%document needs to be modified to load that quantity, and then the 0 in the above expression 
%needs to be replaced by the variable name used.
\end{figure}

>>>>

#place R code here for loading in necessary variables from Results
#ordinarily this would be a readRDS command, but I'm just defining a variable here for now
#allregres<-matrix(rnorm(10),2,5)
M <- readRDS(file="../results_numeric/M.RDS")
rho <- readRDS(file="../results_numeric/rho.RDS")
se3qij <- readRDS(file="../results_numeric/fig3qijmaxse.RDS")
se4qij <- readRDS(file="../results_numeric/fig4qijmaxse.RDS")
@

@@

%***DAN: The code does not yet produce this figure. Eventually it needs to.
%NOTE: I have assumed this figure will look substantially the same as the corresponding main text 
%figure when I wrote the Results. If it does not, then some revisions will be needed.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLBqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig4} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig4} of the main text, but using 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se4qij,5)}, so are not displayed.}\label{fig:fig4_alt}
%***DAN: jasmin, once the se is generated and saved by your code, the chunk at the outset of this 
%document needs to be modified to load that quantity, and then the 0 in the above expression 
%needs to be replaced by the variable name used.
%***JAS:done
\end{figure}
